Continuous developmental change explains discontinuities in word learning

### 2020-03-24 journal/ms_blind.tex
more revisions

\abstract{
``Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change. To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development. However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development. Here we propose a probabilistic model that represents word knowledge in a graded fashion and characterizes developmental change as improvement in the precision of this graded knowledge. Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy. The models' predictions were corroborated by human data we collected from both preschool children and adults. The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.''
}

@@

Many different computational formalisms can represent graded knowledge. Here we use probabilistic models, a formalism that allows both easy examinations of internal representations and quantification of the robustness of these representations. For example, wordform knowledge can be characterized by a probability distribution in a similarity space. The probability is highest at the most typical sound instance of the word. It decreases as the instance becomes less typical. The precision of word knowledge can be characterized by whether it tolerates slightly atypical pronunciations. This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision (for an illustration, see Figure \ref{fig:illus} top and right panels).

@@

In addition to explaining the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task. In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs. \enquote{neem}), the probabilistic distributions do not overlap as much as in the case of similar-sounding words (Figure \ref{fig:illus}, left). This fact means that the learners will have less tolerance for the wrong association, leading to a successful rejection in the Switch task (as was reported by Stager \& Werker (1997) and subsequent studies using the same paradigm). Further, distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).

In this framework, developmental change can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \ref{fig:illus}, right). Importantly, a more precise representation still has a non-zero variance. Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations as was demonstrated in adult studies (Pajak et al., 2016; White et al., 2013).

@@

The probabilistic account was used before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007). However, it is crucial to have a precise computational instantiation of this account which would help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change. One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017). However, this previous work aimed more at reproducing the results of a specific study (Pajak et al., 2016) which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.

The present work proposes a model of word-pair learning and development based on the probabilistic account. We tested the ability of this model to both \emph{explain} various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to \emph{predict} new learning patterns that have not been tested before. In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting recognition difficulty. Although this prediction is intuitive, to our knowledge, it has never been tested. Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.

@@

A similar probabilistic structure was used by Lewis \& Frank (2013) to model concept learning, and by Hofer \& Levy (2017) to model spoken word learning. However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously. In our model, we make the --- more realistic --- assumption that both labels and concepts are characterized with distributions and that the distributions of neighboring categories may overlap. In other words, we allow the model to account for the possibility that an instance of a given category (e.g.,\enquote{bih}) can be mistaken for an instance of a neighboring category (e.g., \enquote{dih}), albeit with a smaller probability. We assume, for simplicity, that this probability is captured by a normal distribution\footnote{We used a normal distribution to simplify the mathematical derivations. This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of accurate responses increases as a function of \(\Delta s\). This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both children (Stager \& Werker, 1997) and adults (Pajak et al., 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases when the representational uncertainty \(\sigma\) decreases. This observation provides a simple model for developmental change. Younger children have noisier representations (see Swingley, 2007; Yoshida et al., 2009), which leads to lower word recognition accuracy, especially for similar-sounding words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases with the visual distance between the semantic referents \(\Delta o\). This is a new prediction that our model makes. Previous work studied the effect of several bottom-up and top-down properties in disambiguating similar sounding words (e.g., Fennell \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007), but to our knowledge, no previous study in the literature tested the effect of the visual distance between the semantic referents.
\end{enumerate}

@@

In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}). More precisely, we explored the predictions related to both distinctiveness and precision. Sound similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied simultaneously in a within-subject design. Two age groups (preschool children and adults) were tested on the same task\footnote{This four-condition within-subject design is relatively novel for preschoolers, but we followed the tablet paradigm (e.g., Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to gather a relatively large number of trials from each child.} to explore whether development can be characterized with the uncertainty parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}

@@

We report data from \(N=\) 63 children ages 4-5 years from a nursery school. An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which is relatively novel for preschoolers, and which was demanding for children. As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) \emph{different} pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2) \emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and \enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts. However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English. Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand. However, this was not the case, word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic). For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults. In this respect, we took inspiration from the work of Pajak et al. (2016). We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.

@@

This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion. We used as a case study the seminal work of Stager \& Werker (1997) showing a discrepancy between children's speech perception abilities and their word learning skills. The development of this discrepancy could be understood in terms of a discrete change in word representation. But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge. Our model instantiates the continuous development hypothesis (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).

More precisely, our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy. On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations. With this assumption, the model was capable of accurately predicting behavior (including around-chance performance in the case of the most difficult contrasts)\footnote{That is, the case when both the sounds and objects are similar for children. Figure 6 shows that the confidence intervals include the chance value of 0.5.}, thus providing a proof of concept for the continuity hypothesis. The discontinuity hypothesis --- which posits the absence of learning and not just retrieval difficulty --- cannot be ruled out by our model, but it is less parsimonious. We propose that the continuous hypothesis should be considered as a baseline; discontinuous development should only be posited if it deviates from this baseline.

@@

While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important. Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded. As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents. This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao, Packard, McMurray, \& Gupta, 2019). Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see Zhao et al. (2019) for a detailed discussion). While we did not model the process of phonological developmental per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.

@@

Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development. It suggests that, all things being equal, children may learn, first, words whose semantic referents are visually different as this allows them to minimize semantic ambiguity. It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space. In addition, it is important to study how laboratory experiment of this sort may explain patterns of word learning in the wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore, Karuza, Giusti, \& Bassett, 2018).

Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002). These two findings are not in contradicton with each other. In this work, and as we explained above, the measured sound uncertainty includes various sources. One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., \enquote{bin} is perceptually different from \enquote{din}), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., \enquote{bin} and \enquote{din} straddle a phonological boundary, that is, they signal a change in meaning. The fact that children have a higher sound uncertainty than adults do, does not necessarily mean this higher uncertainty is due to poorer perceptual encoding, only. In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development. Thus, our finding that children have higher sound-related uncertainty does not contradict previous work showing children are capable of fine-grained speech perception (see Werker \& Curtin (2005) for a similar view).

There are a few limitations to this work. One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old). We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting). Data collection involved presenting participants with several trials across four conditions in a within-subject design. It would have been challenging to obtain such measures with infants. That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months (Fennell \& Byers-Heinlein, 2014; Hazan \& Barrett, 2000; Mattock, Polka, Rvachew, \& Krehm, 2010).

@@

>>>>

\abstract{
Cognitive development is often characterized in terms of discontinuities, but these discontinuities can sometimes be apparent rather than actual and can arise from continuous developmental change. To explore this idea, we use as a case study the finding by Stager and Werker (1997) that children's early ability to distinguish similar sounds does not automatically translate into word learning skills. Early explanations proposed that children may not be able to encode subtle phonetic contrasts when learning novel word meanings, thus suggesting a discontinuous/stage-like pattern of development. However, later work has revealed (e.g., through using more precise testing methods) that children do encode such contrasts, thus favoring a continuous pattern of development. Here we propose a probabilistic model that represents word knowledge in a graded fashion and characterizes developmental change as improvement in the precision of this graded knowledge. Our model explained previous findings in the literature and provided a new prediction --- the referents' visual similarity modulates word learning accuracy. The models' predictions were corroborated by human data collected from both preschool children and adults. The broader impact of this work is to show that computational models, such as ours, can help us explore the extent to which episodes of cognitive development that are typically thought of as discontinuities may emerge from simpler, continuous mechanisms.
}

@@

Many different computational formalisms can represent graded knowledge. Here we use probabilistic models, a formalism that allows both easy examinations of internal representations and quantification of the robustness of these representations. Our goal here is an exploration at the highest level of abstraction, in which we attempt to characterize the computational constraints that might lead to a particular behavior (Marr, 1982). We characterize word knowledge by a probability distribution in a similarity space. The probability is highest at the most typical sound instance of the word. It decreases as the instance becomes less typical. The precision of word knowledge can be characterized by whether it tolerates slightly atypical pronunciations. This tolerance is captured formally by the variance of the probability distribution: larger variance indicates higher tolerance and lower precision, whereas smaller variance indicates lower tolerance and higher precision (for an illustration, see Figure \ref{fig:illus} top and right panels).

@@

In addition to providing a potential explanation of the difference in behavior across the Switch and the preferential looking tasks, the probabilistic account explains differences in behavior within the same task. In particular, when the labels are quite distinct in the perceptual space (\enquote{lif} vs. \enquote{neem}), the probabilistic distributions do not overlap as much as in the case of similar-sounding words (Figure \ref{fig:illus}, left). This fact means that the learners will have less tolerance for the wrong association, leading to a successful rejection in the Switch task (as was reported by Stager \& Werker (1997) and subsequent studies using the same paradigm). Further, distinctiveness can be enhanced even for minimally different sounds when other cues highlight their difference (Dautriche, Swingley, \& Christophe, 2015; Rost \& McMurray, 2009, 2010; Thiessen, 2007; Yeung \& Werker, 2009).

In this framework, developmental change can be understood as an increase in the precision (i.e., a decrease in the variance) of the probabilistic knowledge, leading to a lower overlap between the distributions of similar-sounding words (Figure \ref{fig:illus}, right). Importantly, a more precise representation still has a non-zero variance. Thus, learning difficulties can still be induced with challenging stimuli or in cognitively demanding situations, as has been demonstrated in adult studies (Pajak et al., 2016; White et al., 2013).

@@

A probabilistic account has been described before to explain patterns of learning and development at the qualitative level (e.g., Swingley, 2007). However, it is crucial to have a precise computational instantiation of this account which can help us 1) test this theoretical hypothesis more directly and 2) identify the particular parameters that are the locus of developmental change. One previous study attempted to provide such a computational instantiation (Hofer \& Levy, 2017). However, this previous work aimed more at reproducing the results of a specific study (Pajak et al., 2016), which focused on explaining the mismatch between speech perception and word learning in adults rather than on exploring the mechanism of development.

The present work proposes a model of developmental change in word-pair learning based on the probabilistic account. We tested the ability of this model to both \emph{explain} various findings in previous experiments in both children and adults (e.g., the fact that similar words are harder to learn than different words) and to \emph{predict} new learning patterns that have not been tested before. In particular, we test the prediction that referent similarity (i.e., the confusability of pictures referred to by novel words) should play an identical computational role to word form similarity in predicting word recognition difficulty.
Previous work in this line of research has studied the effect of several bottom-up and top-down properties on improving learning (e.g., Fennell \& Waxman, 2010; Rost \& McMurray, 2009; Thiessen, 2007) but the effect of the referent similarity remains to be tested. While some researchers studied this effect on wordform learning (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao, Packard, McMurray, \& Gupta, 2019), to our knowledge, the effect on children's word-object mapping has not been investigated before. Finally, we explore the extent to which the probabilistic account allows us to understand development in terms of as a continuous refinement in similar representations across the lifespan.

@@

A similar probabilistic structure was used by Lewis \& Frank (2013) to model concept learning, and by Hofer \& Levy (2017) to model spoken word learning. However, the first study assumed that the sounds are heard unambiguously, and the second assumed the concepts are observed unambiguously. In our model, we make the --- more realistic --- assumption that both labels and concepts are characterized with distributions and that the distributions of neighboring categories may overlap. In other words, we allow the model to account for the possibility that an instance of a given category (e.g.,\enquote{bih}) can be mistaken for an instance of a neighboring category (e.g., \enquote{dih}), albeit with a smaller probability. We assume, for simplicity, that this probability is captured by a normal distribution\footnote{We used a normal distribution to simplify the mathematical derivations. This is obviously not aimed at providing a precise representation for the word-forms (and even less so for the visual objects), but as we shall see in the results section, this simplified representation was enough to quantify the confusability of a given stimulus with its neighbors, which is the quantity we needed to predict the accuracy of word-object mapping in our task.}:

@@

\begin{enumerate}
\def\labelenumi{\arabic{enumi})}
\item
  For fixed values of \(\Delta o\) and \(\sigma\), the probability of accurate responses increases as a function of \(\Delta s\). This pattern accounts for the fact that similar sounds are generally more challenging to learn than different sounds for both children (Stager \& Werker, 1997) and adults (Pajak et al., 2016).
\item
  For fixed values of \(\Delta s\) and \(\Delta o\), accuracy increases when the representational uncertainty \(\sigma\) decreases. This observation provides a simple model for developmental change. Younger children have noisier representations (see Swingley, 2007; Yoshida et al., 2009), which leads to lower word recognition accuracy, especially for similar-sounding words.
\item
  For fixed values of \(\Delta s\) and \(\sigma\), accuracy increases with the visual distance between the semantic referents \(\Delta o\).
\end{enumerate}

@@

In this experiment, we tested participants in the word learning task introduced above (Figure \ref{fig:task}). More precisely, we explored the predictions related to both distinctiveness and precision. Sound similarity (\(\Delta s\)) and object similarity (\(\Delta o\)) were varied simultaneously in a within-subject design. Two age groups (preschool children and adults) were tested on the same task\footnote{This four-condition within-subject design is somewhat unusual for preschoolers, but we followed the tablet paradigm (e.g., Frank, Sugarman, Horowitz, Lewis, \& Yurovsky, 2016) which allowed us to gather a relatively large number of trials from each child.} to explore whether development can be characterized with the uncertainty parameters, \(\sigma_C\) and \(\sigma_L\). The experiment, sample size, exclusion criteria, and the model's main predictions were pre-registered.\footnote{Due to the double-blind review, the link to the osf repository is only provided in the full version addressed to the editor.}

@@

We report data from \(N=\) 63 children ages 4-5 years from a nursery school. An additional \(N=\) 39 children participated but were removed from analyses using a preregistered exclusion criterion of not being above chance on the catch trials.\footnote{The number of children who were excluded is a bit high for this age group. This is partly due to our adoption of a 2x2 fully within-subject design, which was demanding for children. As we explain below, we adopted this design based on pilot testing that indicated that precision of measurement was critical for testing our experimental predictions.} We also report data from \(N=\) 74 adult participants tested on Amazon Mechanical Turk. An additional \(N=\) 26 were tested but removed from analyses using preregistered exclusion criteria of either having a low score on the catch trials or being familiar with the non-English sound stimuli we used in the adult experiment.

@@

The sound stimuli were generated using the MBROLA Speech Synthesizer (Dutoit, Pagel, Pierret, Bataille, \& Van der Vrecken, 1996). We generated three kinds of nonsense word pairs which varied in their degree of perceptual similarity to English speakers: 1) \emph{different} pairs: \enquote{lif}/\enquote{neem} and \enquote{zem}/\enquote{doof}, 2) \emph{intermediate} pairs: \enquote{aka}/\enquote{ama} and \enquote{ada}/\enquote{aba}, and 3) \emph{similar} non-English pairs\footnote{For the intermediate/similar pairs, we made the choice of using a VCV (Vowel-Consonant-Vowel) structure in order to emphasize the phonemic difference in the minimal pairs, especially for the non-native contrasts. However, as one reviwer rightfully pointed out to us, this structure could influence word leaning performance since it is not common in English. Nevertheless, if we observed this effect, we would have seen differences in predictability between the intermediate/similar pairs on the one hand, and different pairs (which are phonotactically common in English) on the other hand. However, this was not the case; word learning accuracy was correctly predicted based on perceptual similarity alone.}: \enquote{ada}/\enquote{a\textipa{d\super h}a} (in hindi) and \enquote{a\textipa{Q}a}/\enquote{a\textipa{\textcrh}a} (in arabic). For the similar pairs, we used non-native sounds because this was a good way to decrease perceptual similarity for adults. In this respect, we took inspiration from the work of Pajak et al. (2016). We refer the reader to that paper for a lengthy discussion of the literature on (and implications for) L2 phoneme perception.

@@

This paper explored the idea that some seemingly stage-like patterns in cognitive development can be characterized in a continuous fashion. We used as a case study the seminal work of Stager \& Werker (1997) showing a discrepancy between children's speech perception abilities and their word learning skills. The development of this discrepancy could be understood in terms of a discrete change in word representation. But our model demonstrates that it can also be parsimoniously described as a result of continuous developmental change in the precision of children's graded word knowledge. Our model thus provides a computational instantiation and test of the continuous development hypothesis proposed in previous work (Pajak et al., 2016; Swingley, 2007; Yoshida et al., 2009).

Our model used the assumption that the ability to distinguish two sounds perceptually leads to an accurate mapping of these sounds with two distinct objects, although this mapping can be noisy. On this account, apparent patterns of failure and success in retrieval tasks (such as ours) reflect different degrees of noise in the learned representations and not necessarily the presence/absence of these representations. With this assumption, the model was capable of accurately predicting behavior (including around-chance performance in the case of the most difficult contrasts)\footnote{That is, the case when both the sounds and objects are similar for children. Figure 6 shows that the confidence intervals include the chance value of 0.5.}, thus providing a proof of concept for the continuity hypothesis. The discontinuity hypothesis --- which posits the absence of learning and not just retrieval difficulty --- cannot be ruled out by our model, but it is less parsimonious. We propose that the continuous hypothesis should be considered as a baseline; discontinuous development should only be posited if it deviates from this baseline.

@@

While most research has focused on sound representation specifically in analyzing the process of learning similar-sounding words, this work showed that the visual representation of the referent is equally important. Indeed, Model 1 --- which assumes that any visually discriminable contrast can be encoded unambiguously as separate referents --- failed to explain the data, whereas Model 2 and 3 --- which take into account visual ambiguity --- succeeded. As a consequence of this assumption, we found that just like word learning is modulated by the phonological similarity of the form, it is also modulated by the visual similarity of the semantic referents. This result is different from previous findings on the effect of the referents' similarity on the phonological development of the wordform (Fourtassi \& Dupoux, 2019; Yeung \& Werker, 2009; Zhao et al., 2019). Our result is about wordform-referent mapping --- a different learning problem as it involves, in particular, the encoding of visual semantic/referent knowledge about the word (see Zhao et al. (2019) for a detailed discussion). While we did not model the process of phonological development per se, we argued in our discussion above that part of the observed difference between children and adults in terms of their word-referent mapping skills can be attributed to phonological development.

@@

Our finding that word learning is mediated by the visual similarity of the semantic objects has implications for theories of lexical development. It suggests that, all things being equal, children may learn, first, words whose semantic referents are visually different as this allows them to minimize semantic ambiguity. It will be interesting for future work to explore whether the results that we obtained using visual similarity generalize to richer, more conceptual features in the semantic space. In addition, it is important to study how laboratory experiments of this sort may explain patterns of word learning in the wild (Engelthaler \& Hills, 2017; Fourtassi, Bian, \& Frank, 2018; Sizemore, Karuza, Giusti, \& Bassett, 2018).

Our work found, among other things, that children have higher sound/phoneme uncertainty than adults do, but prior work have shown that children have good auditory encoding (Swingley, 2003; Swingley \& Aslin, 2000, 2002). These two findings are not in conflict with each other. In this work, and as we explained above, the measured sound uncertainty includes various sources. One of these sources is perceptual uncertainty, i.e., the ability to perceptually distinguish a sound from other neighboring sounds (e.g., \enquote{bin} is perceptually different from \enquote{din}), and another source is categorical uncertainty, i.e., the ability to estimate phonological boundaries, e.g., \enquote{bin} and \enquote{din} straddle a phonological boundary, that is, they signal a change in meaning. The fact that children have a higher sound uncertainty than adults do, does not necessarily mean this higher uncertainty is due to poorer perceptual encoding only. In fact, it is possible that much of the differential in uncertainty (compared to adults) is due to the categorical/phonological dimension which we know undergoes a process of reorganization and refinement across development. Thus, our finding that children have higher sound-related uncertainty does not contradict previous work showing children are capable of fine-grained speech perception (see Werker \& Curtin (2005) for a similar view).

There are a number of limitations to this work. One is that the model was fit to data from children at a relatively older age (4-5 years old) than what is typically studied in the literature (14-17 month-old). We selected this older age group to optimize the number and precision of the experimental measures (both are crucial to model fitting). Data collection involved presenting participants with several trials across four conditions in a within-subject design. It would have been challenging to obtain such measures with infants. That said, though we used data from older children, we still found clear developmental differences with adults, confirming and extending findings that the ability to distinguish similar-sounding words continues developing well beyond 17 months (Fennell \& Byers-Heinlein, 2014; Hazan \& Barrett, 2000; Mattock, Polka, Rvachew, \& Krehm, 2010).

@@

\leavevmode\hypertarget{ref-marr1982}{}%
Marr, D. (1982). \emph{Vision}. WH Freeman.
